Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-22 doc/Paper/main.tex
some changes

    It is worth noting that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$. This prior was estimated as the scatter between the best-fit shift parameters that recover the same shear power spectrum for different estimates of the redshift distribution and different photo-$z$ codes. We carried out an additional analysis where we quantified the shift and width parameters allowed by the sample variance uncertainties in our fiducial estimate of the redshift distribution from COSMOS. To do so, we estimated the covariance matrix of the redshift distribution amplitudes in each narrow histogram bin shown in Fig. \ref{fig:nzs} using a simplified linear bias model. From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean), and compute the mean redshift of each realization. Estimating the standard deviation in the mean redshift of all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.  We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties. It is interesting to note that, having access to the covariance matrix of the redshift distribution would allow us to perform a more general characterization of the $N(z)$ uncertainties, beyond shift-width parametrizations (e.g. through principal component analysis). We leave this type of study for future work.

@@

    We anticipate that these results will be useful for forecasting the  constraining power of magnitude-limited samples. \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?} \todo{DA: I'd suggest adding Andrina's latest plot with the SRD lines to Figure \ref{fig:HOD-redshift} to avoid new figures.} An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula. Our full parameter chains for the different limiting magnitudes are available upon request. \as{Is this the case?} \an{That would be totally fine with me.}
    %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
    \begin{figure}
      \begin{center}
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}. The shaded regions denote the $68 \%$ c.l..}
        \label{fig:magnitude-cuts-bias}
      \end{center}
    \end{figure}

>>>>

    It is worth noting that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$. This prior was estimated as the scatter between the best-fit shift parameters that recover the same shear power spectrum for different estimates of the redshift distribution and different photo-$z$ codes. We carried out an additional analysis where we quantified the shift and width parameters allowed by the sample variance uncertainties in our fiducial estimate of the redshift distribution from COSMOS. To do so, we estimated the covariance matrix of the redshift distribution amplitudes in each narrow histogram bin shown in Fig. \ref{fig:nzs} assuming a simple cylindrical survey geometry and that volume-to-volume number density correlations follow a normal distribution given a biased linear power spectrum. From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean). For each realization, we compute the mean and the width of corresponding $N(z)$ distributions. Estimating the standard deviation in the means and widths from all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.  We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties. It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance, beyond the simple shift-width parametrizations (e.g. through principal component analysis). We leave this type of study for future work.

@@

    We anticipate that these results will be useful for forecasting the  constraining power of magnitude-limited samples. \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?} \todo{DA: I'd suggest adding Andrina's latest plot with the SRD lines to Figure \ref{fig:HOD-redshift} to avoid new figures.} An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula. Our full parameter chains with full halo model parameterization for the different limiting magnitudes are available upon request. 
    %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
    \begin{figure}
      \begin{center}
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}. The shaded regions denote the $68 \%$ c.l..}
        \label{fig:magnitude-cuts-bias}
      \end{center}
    \end{figure}
